---
title: "ms_results"
author: "Jessica Gephart"
output: html_document
---

```{r, echo=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
# Load packages
library(tidyverse)
library(countrycode)
library(kableExtra)
library(ggpubr)
library(tidytext)
```

```{r load_data}
# Directory
datadir <- "outputs"

global_export_by_source <- read.csv(file.path(datadir, "global_export_by_source.csv"))
all_degree_summary <- read.csv(file.path(datadir, "all_degree_summary.csv"))
habitat_method_degree_summary <- read.csv(file.path(datadir, "habitat_method_degree_summary.csv"))
```

# Trends blue food globalization

```{r trends_summary}
# Generate stats for text
total_1996 <- round(sum(global_export_by_source %>% filter(year == 1996) %>% pull(live_weight_t))/1000000, 1)
total_2019 <- round(sum(global_export_by_source %>% filter(year == 2019) %>% pull(live_weight_t))/1000000, 1)
total_2020 <- round(sum(global_export_by_source %>% filter(year == 2020) %>% pull(live_weight_t))/1000000, 1)

total_capture_1996 <- round(sum(global_export_by_source %>% filter(year == 1996, str_detect(habitat_method, "capture")) %>% pull(live_weight_t))/1000000, 1)
total_capture_2019 <- round(sum(global_export_by_source %>% filter(year == 2019, str_detect(habitat_method, "capture")) %>% pull(live_weight_t))/1000000, 1)

# Total trade by environment and production method
# Total trade for marine capture
total_marine_capture_1996 <- round(sum(global_export_by_source %>% filter(year == 1996, str_detect(habitat_method, "marine capture")) %>% pull(live_weight_t))/1000000, 1)
total_marine_capture_2019 <- round(sum(global_export_by_source %>% filter(year == 2019, str_detect(habitat_method, "marine capture")) %>% pull(live_weight_t))/1000000, 1)
total_inland_capture_1996 <- round(sum(global_export_by_source %>% filter(year == 1996, str_detect(habitat_method, "inland capture")) %>% pull(live_weight_t))/1000000, 1)
total_inland_capture_2019 <- round(sum(global_export_by_source %>% filter(year == 2019, str_detect(habitat_method, "inland capture")) %>% pull(live_weight_t))/1000000, 1)
# Total trade for marine aquaculture
total_marine_aquaculture_1996 <- round(sum(global_export_by_source %>% filter(year == 1996, str_detect(habitat_method, "marine aquaculture")) %>% pull(live_weight_t))/1000000, 1)
total_marine_aquaculture_2019 <- round(sum(global_export_by_source %>% filter(year == 2019, str_detect(habitat_method, "marine aquaculture")) %>% pull(live_weight_t))/1000000, 1)
# Total trade for inland aquaculture
total_inland_aquaculture_1996 <- round(sum(global_export_by_source %>% filter(year == 1996, str_detect(habitat_method, "inland aquaculture")) %>% pull(live_weight_t))/1000000, 1)
total_inland_aquaculture_2019 <- round(sum(global_export_by_source %>% filter(year == 2019, str_detect(habitat_method, "inland aquaculture")) %>% pull(live_weight_t))/1000000, 1)

# Total trade for all capture
total_capture_1996 <- round(sum(global_export_by_source %>% filter(year == 1996, str_detect(habitat_method, "capture")) %>% pull(live_weight_t))/1000000, 1)
total_capture_2019 <- round(sum(global_export_by_source %>% filter(year == 2019, str_detect(habitat_method, "capture")) %>% pull(live_weight_t))/1000000, 1)
total_capture_2020 <- round(sum(global_export_by_source %>% filter(year == 2020, str_detect(habitat_method, "capture")) %>% pull(live_weight_t))/1000000, 1)

# Total trade for all aquaculture
total_aquaculture_1996 <- round(sum(global_export_by_source %>% filter(year == 1996, str_detect(habitat_method, "aquaculture")) %>% pull(live_weight_t))/1000000, 1)
total_aquaculture_2019 <- round(sum(global_export_by_source %>% filter(year == 2019, str_detect(habitat_method, "aquaculture")) %>% pull(live_weight_t))/1000000, 1)
total_aquaculture_2020 <- round(sum(global_export_by_source %>% filter(year == 2020, str_detect(habitat_method, "aquaculture")) %>% pull(live_weight_t))/1000000, 1)

# Total trade for FMFO
artis_fm <- read.csv(file.path(datadir, "artis_fm.csv"))

total_fmfo_1996 <- artis_fm %>%
  filter(year == 1996) %>%
  mutate(live_weight_t = live_weight_t/1000000) %>%
  pull(live_weight_t)

total_fmfo_2019 <- artis_fm %>%
  filter(year == 2019) %>%
  mutate(live_weight_t = live_weight_t/1000000) %>%
  pull(live_weight_t)

```

```{r percent_export_by_source_trends}
percent_export_by_source <- read.csv(file.path(datadir, "domestic_export_percent_production_by_habitat_method.csv"))
percent_export_total <- read.csv(file.path(datadir, "total_export_percent_prod.csv"))
percent_export_total_dom_1996 <- percent_export_total %>% 
  filter(year == 1996, calc_type == "domestic exports") %>% 
  pull(percent_export)
percent_export_total_dom_2019 <- percent_export_total %>% 
  filter(year == 2019, calc_type == "domestic exports") %>% 
  pull(percent_export)
percent_export_total_1996 <- percent_export_total %>% 
  filter(year == 1996, calc_type == "all export sources") %>% 
  pull(percent_export)
percent_export_total_2019 <- percent_export_total %>% 
  filter(year == 2019, calc_type == "all export sources") %>% 
  pull(percent_export)
percent_marine_capture_exported_1996 <- percent_export_by_source %>% 
  filter(year == 1996, habitat_method == "marine capture") %>%
  pull(percent_export)
percent_marine_capture_exported_2019 <- percent_export_by_source %>% 
  filter(year == 2019, habitat_method == "marine capture") %>%
  pull(percent_export)
percent_marine_aqua_exported_1996 <- percent_export_by_source %>% 
  filter(year == 1996, habitat_method == "marine aquaculture") %>%
  pull(percent_export)
percent_marine_aqua_exported_2019 <- percent_export_by_source %>% 
  filter(year == 2019, habitat_method == "marine aquaculture") %>%
  pull(percent_export)
percent_inland_capture_exported_1996 <- percent_export_by_source %>% 
  filter(year == 1996, habitat_method == "inland capture") %>%
  pull(percent_export)
percent_inland_capture_exported_2019 <- percent_export_by_source %>% 
  filter(year == 2019, habitat_method == "inland capture") %>%
  pull(percent_export)
percent_inland_aqua_exported_1996 <- percent_export_by_source %>% 
  filter(year == 1996, habitat_method == "inland aquaculture") %>%
  pull(percent_export)
percent_inland_aqua_exported_2019 <- percent_export_by_source %>% 
  filter(year == 2019, habitat_method == "inland aquaculture") %>%
  pull(percent_export)
```

```{r trends_concentration}
# Export / Imports concentration
cumulative_percent_threshold <- 75
export_concentration_n_countries <- read.csv(file.path(datadir, "export_concentration_n_countries.csv"))

import_concentration_n_countries <- read.csv(file.path(datadir, "import_concentration_n_countries.csv"))
```

```{r degree_summary_stats}
all_degree_1996 <- all_degree_summary %>%
  filter(year == 1996) %>% 
  summarise(all_out_degree = mean(all_out_degree, na.rm = TRUE)) %>%
  pull(all_out_degree)
all_degree_2019 <- all_degree_summary %>%
  filter(year == 2019) %>% 
  summarise(all_out_degree = mean(all_out_degree, na.rm = TRUE)) %>%
  pull(all_out_degree)
```


## Text for MS

Globalization describes the degree of international connectedness, which can be characterized by the increasing flow of goods and number of trade relationships. Aquatic foods became increasingly globalized from 1996-2019, with exports increasing `r round(100*((total_2019-total_1996)/total_1996),0)`%  (from `r total_1996` to `r total_2019` mil t; Fig 1a) and the average number of export partners increasing `r round(100*((all_degree_2019-all_degree_1996)/all_degree_1996),0)`%  (from `r round(all_degree_1996, 1)` to `r round(all_degree_2019, 1)`; Fig 4c) since 1996. Over that period, both farmed and wild exports increased, though aquaculture exports grew faster, more than tripling, whereas capture exports grew by `r round(100*((total_capture_2019-total_capture_1996)/total_capture_1996),0)`%. Corresponding with the first year of the COVID-19 pandemic, global aquatic food exports declined `r -1*round(100*((total_2020-total_2019)/total_2019),1)`% overall in 2020 relative to 2019, with a `r -1*round(100*((total_capture_2020-total_capture_2019)/total_capture_2019),1)`% decline in capture exports, but a `r round(100*((total_aquaculture_2020-total_aquaculture_2019)/total_aquaculture_2019),1)`% increase in aquaculture exports (Fig 1a). Despite aquaculture now comprising half of blue food production, capture fishery products still dominate blue food exports, with capture products responsible for `r 100*round(total_capture_2019/total_2019, 1)`% of exports. Marine-sourced products dominate both capture and aquaculture exports, comprising `r round(100*total_marine_capture_2019/(total_marine_capture_2019+total_inland_capture_2019), 1)`% and `r round(100*total_marine_aquaculture_2019/(total_marine_aquaculture_2019+total_inland_aquaculture_2019), 1)`%, respectively. Aquatic food trade outpaced fishmeal (for non-human consumption) trade, which remained relatively stable, declining `r abs(round(100*(total_fmfo_2019-total_fmfo_1996)/(total_fmfo_1996), 1))`% over the time period. Consequently, fishmeal exports as a share of the sum of aquatic food and fishmeal exports declined from `r abs(round(100*(total_fmfo_1996)/(total_1996+total_fmfo_1996), 1))`% in 1996 to only `r abs(round(100*(total_fmfo_2019)/(total_2019+total_fmfo_2019), 1))`% in 2019. 

Another measure of the degree of globalization is the share of production exported. Domestic exports, which represent exports sourced from that nation’s production irrespective of where their production occurred, increased to `r round(percent_export_total_dom_2019, 1)`% of production in 2019 while total exports, which represents domestic plus exports of foreign and unknown origin, reached `r round(percent_export_total_2019, 1)`% of all production. For comparison, the share of cereal production exported grew from around 10% in the late 1990s to 17% in the 2020s (Clapp 2022). Marine capture products have the greatest share of production destined for export (domestic exports represented `r round(percent_marine_capture_exported_2019, 1)`% of production) and experienced the largest increases in the share exported, while inland aquaculture had the lowest share of production destined for export (domestic exports represented only `r round(percent_inland_aqua_exported_2019, 1)`% of production) (Fig 1b). 

Globalization may create systemic risks from shocks, particularly when trade is highly concentrated. Since 1996, aquatic food exports and imports have become moderately less concentrated, with only `r export_concentration_n_countries %>% filter(year == 1996) %>% pull(n)` countries comprising `r cumulative_percent_threshold`% of exports in 1996 versus `r export_concentration_n_countries %>% filter(year == 2019) %>% pull(n)` countries in 2019. Compare this with crops where just 7 countries and the EU account for 90% of wheat exports and just four countries accounting >80% of maize exports (Clapp 2022). The declining concentration is driven by capture fishery exports, whereas both inland and marine aquaculture exports became somewhat more concentrated (Fig SX). Aquaculture exports are generally concentrated among fewer countries than capture exports, corresponding to the high concentration of aquaculture production. Import concentration declined more dramatically, with `r import_concentration_n_countries %>% filter(year == 1996) %>% pull(n)` countries comprising `r cumulative_percent_threshold`% of imports in 1996 versus `r import_concentration_n_countries %>% filter(year == 2019) %>% pull(n)` countries in 2019 (Fig SX). The more dispersed import patterns are likely associated with expanding middle classes and urbanization, particularly in low- and middle-income countries, which are responsible for increasing aquatic food demand in many countries (Naylor et al. 2021; SOFIA 2022). 

![Figure 1: Increases in global export of aquatic foods. a) Exports of global marine and freshwater aquaculture and fishery products (t live weight equivalent) from 1996-2019. b) Percent of global marine and freshwater aquaculture and fishery production exported, excluding re-exports. c) Out degree by production method and environment.](outputs/fig1.png)


## Other summary stats
Global seafood trade increased from `r total_1996` million t (live weight) in 1996 to `r total_2019` million t (live weight) in 2019, representing a `r round(100*((total_2019-total_1996)/total_1996),0)`% increase over that period.

Global capture fishery trade increased from `r total_capture_1996` million t (live weight) in 1996 to `r total_capture_2019` million t (live weight) in 2019, representing a `r round(100*((total_capture_2019-total_capture_1996)/total_capture_1996),0)`% increase over that period. In 1996, capture fishery trade represented `r round(100*total_capture_1996/total_1996)`% of all seafood exports and by 2019 capture fishery exports represented `r round(100*total_capture_2019/total_2019)`% of all seafood exports. 

Global aquaculture fishery trade increased from `r total_aquaculture_1996` million t (live weight) in 1996 to `r total_aquaculture_2019` million t (live weight) in 2019, representing a `r round(100*((total_aquaculture_2019-total_aquaculture_1996)/total_aquaculture_1996),0)`% increase over that period. In 1996, aquaculture fishery trade represented `r round(100*total_aquaculture_1996/total_1996)`% of all seafood exports and by 2019 capture fishery exports represented `r round(100*total_aquaculture_2019/total_2019)`% of all seafood exports.

Aquatic foods have become increasingly globalized, with the percent of production exported increasing by `r 100*round((percent_export_total_dom_2019-percent_export_total_dom_1996)/percent_export_total_dom_1996, 1)` and the volume and number of trade partnerships approximately doubling. However, trends differ across aquatic food groups, with marine capture remaining the most highly globalized group, but with marine aquaculture showing faster trade growth.

# Shifts in global flows of blue foods

```{r}
bilateral_flow_change <- read.csv(file.path(datadir, "bilateral_flow_change.csv"))

percent_flow_increases <- 100*(nrow(bilateral_flow_change %>% filter(change > 0)))/nrow(bilateral_flow_change)
```

## Text for MS

The top importers, exporters, and bilateral flows vary by production method, underscoring the importance of disaggregating aquatic food trade (Fig SX). In recent years, the marine capture and aquaculture trade networks have been dominated by Asia and Europe, and to a lesser extent, North America (Fig SX). Since 1996, the marine trade networks shifted more toward Asia and Europe, with large increases in marine capture imports and exports by Africa and large increases in marine aquaculture exports from South America and imports to North America (Fig SX). At the country level, although some countries rank among the top traders across production methods, such as China for exports and the USA for imports, many countries are only top traders for one production method. Meanwhile, inland farmed and wild production is oriented more toward domestic consumption and what is exported tends to stay within the region, particularly within Asia (Fig 2; Fig SX). Inland aquatic food trade is dominated by aquaculture, with the highest exports from Vietnam and China and highest imports by the United States, Japan, and South Korea (Fig SX).

Intraregional trade tends to be higher than interregional trade due to shorter transport distances, historical ties, and established regional trade agreements (REF). This pattern generally holds for aquatic food trade as intraregional trade is the highest or second highest for all regions other than Oceania and South America. Our disaggregated trade network is based on a reconciled version of reported trade (Gaulier and Zignago 2010) and therefore does not capture informal and unreported trade networks that often exist among neighboring countries, notably in Africa (Benassi et al. 2019). Since 1996, trade increased between nearly all regional trade pairs, other than South America to Europe and Asia and within North America. At the country level, trade increased between `r round(percent_flow_increases, 1)`% of trade pairs. Despite trade increasing with partners across the globe, regional trade within Asia, Europe and Africa outpaced interregional trade with those regions. The largest average annual growth increases occurred for trade within Asia and within Europe, followed by trade between Europe and Asia. 

Least developed countries, as defined by the UN, are net exporters of aquatic foods across all production methods, with net exports more than tripling between 1996 and their peak in 2018 (Fig SX). The pattern is largely driven by marine capture products, which nearly quadrupled, while other aquatic food sector net exports remained relatively stable. Net exports of aquatic foods may be beneficial to least developed countries where high value species are exported and revenue used to purchase other foods (Asche et al, 2015). However, recent work exploring movement of nutrients derived from fisheries suggests international trade is driving redistribution of essential micronutrients prevalent and bioavailable in aquatic foods from areas of high deficiency in middle and low income countries to developed nations with greater nutrient security (Nash et al, 2022). Further, Nash et al (2022) found evidence of high vulnerability to future shifts in trade practices among middle and low income nations currently benefiting from trade in aquatic foods; high net imports are associated with the risk of receiving shocks propagated through trade (Gephart et al. 2016). 

![Figure 2: Regional trade flows by trade partner and production source. a) Total imports to each region colored by trade partner. b) Bilateral flows colored by production method and habitat source. c) Total exports from each region colored by trade partner. Values represent million tonnes in live weight equivalents.](outputs/fig2.png)

## Other summary stats


# National blue food supplies
```{r}
supply <- read.csv(file.path(datadir, "supply.csv"))

global_supply <- read.csv(file.path(datadir, "global_supply.csv"))

global_supply_1996 <- global_supply %>%
  filter(year == 1996) %>%
  pull(supply_no_error)

global_supply_2020 <- global_supply %>%
  filter(year == 2020) %>%
  pull(supply_no_error)

habitat_method_supply <- read.csv(file.path(datadir, "habitat_method_supply.csv"))

tmp <- habitat_method_supply %>%
  select(habitat, method, year, supply_no_error) %>%
  filter(year == 1996 | year == 2020) %>%
  mutate(year = paste("year", year, sep = "_")) %>%
  pivot_wider(names_from = year, values_from = supply_no_error) %>%
  mutate(percent_diff = 100 * (year_2020 - year_1996) / year_1996)

inland_aqua_supply_change <- tmp %>%
  filter(habitat == "inland" & method == "aquaculture") %>%
  pull(percent_diff)

marine_aqua_supply_change <- tmp %>%
  filter(habitat == "marine" & method == "aquaculture") %>%
  pull(percent_diff)

marine_cap_supply_change <- tmp %>%
  filter(habitat == "marine" & method == "capture") %>%
  mutate(percent_diff = abs(percent_diff)) %>%
  pull(percent_diff)

marine_cap_supply_percent <- habitat_method_supply %>%
  filter(year == 2020) %>%
  filter(percent_supply == max(percent_supply)) %>%
  pull(percent_supply)

regional_method_supplies <- read.csv(file.path(datadir, "regional_method_supplies.csv"))

oceania_cap_supply_percent <- regional_method_supplies %>%
  filter(region == "Oceania") %>%
  pull(capture)

asia_cap_supply_percent <- regional_method_supplies %>%
  filter(region == "Asia") %>%
  pull(capture)

method_supplies <- read.csv(file.path(datadir, "method_supplies.csv"))

cap_supply_percent <- method_supplies %>%
  filter(method == "capture") %>%
  pull(percent_supply)

consumption_foreign <- read.csv(file.path(datadir, "consumption_foreign.csv"))

foreign_consumption_start <- consumption_foreign %>%
  filter(year == 1996) %>%
  pull(percent_supply)

foreign_consumption_end <- consumption_foreign %>%
  filter(year == 2020) %>%
  pull(percent_supply)

asia_farmed_year <- supply %>%
  filter(region == "Asia") %>%
  group_by(year, method) %>%
  summarize(supply_no_error = sum(supply_no_error)) %>%
  ungroup() %>%
  filter(method == "capture" | method == "aquaculture") %>%
  pivot_wider(names_from = method, values_from = supply_no_error) %>%
  filter(aquaculture > capture) %>%
  filter(year == min(year)) %>%
  pull(year)

```

## Text for MS

Since direct measurements of consumption are not collected globally, our understanding of global consumption patterns are based on apparent consumption, which generally represents the sum of production and imports minus exports and waste. Consequently, trade is central to estimating consumption and the resolution of consumption patterns is limited by the resolution of the production and trade data. By estimating species level trade, we are able to estimate apparent consumption of blue foods by species and production method. 

Globally, blue food consumption increased from `r signif(global_supply_1996, digit = 3)` (million tonnes) in 1996 to `r signif(global_supply_2020, digit = 3)` (million tonnes) in 2020. Blue food consumption also increased across all regions outside of South America, where per capita blue food consumption decreased X%, from X% in 1996 to Y% in 2020. [say this is supply included non food uses] [Double check that FMFO was excluded and discuss this pattern]. Most of the global increase was from inland and marine aquaculture, which increased by `r signif(inland_aqua_supply_change, digits = 3)` and `r signif(inland_aqua_supply_change, digits = 3)`%, respectively, over that period while marine capture consumption declined by `r signif(marine_cap_supply_change, digits = 1)`%. Capture still makes up `r signif(cap_supply_percent, digits = 2)`% of global blue food consumption and its contribution to regional blue food supplies ranges from `r signif(oceania_cap_supply_percent, digits = 2)`% in Oceania to `r signif(asia_cap_supply_percent, digits = 2)`% in Asia, where farmed consumption overtook wild consumption in `r asia_farmed_year`.

High reliance on foreign-sourced foods can pose a food security risk, motivating policies to protect domestic supplies such as the development of grain stocks and support for domestic food production (REFs). For example, high seafood import dependence in the US was used to propose a suite of policy changes to boost domestic production, including expanding aquaculture production and opening marine protected areas to fishing (Gephart et al. 2019). Since we estimate exports from domestic and foreign sources, we are able to track changes in reliance on foreign sourced products. Globally, the share of consumption that is foreign sourced has increased from `r signif(foreign_consumption_start, digits = 3)`% to `r signif(foreign_consumption_end, digits = 3)`% (Fig 3c), but patterns vary across regions with Asia and S America dominated by domestic supply, but Europe dominated by foreign supply (Fig 3d). [Add points about patterns across production methods].
	
The diversity of blue food production globally enables high diversity in blue food consumption. However, one concern about food trade is that it leads to homogenization of diets (REFS). To explore this issue, we compared the diversity (represented by the Shannon index) of production versus imports and domestic supply versus foreign supply, as well as the diversity of total supply versus total import volume (Fig 4). One notable limitation of this measure of supply diversity is that instances where production or trade is only estimated at the genus or higher level will be interpreted in the calculation as a single species. Consequently, countries with low species resolution will generally appear to have less diverse production, limiting the ability to compare supply diversity across countries.  
We find that across all regions and over time, production diversity is higher than import diversity (Fig 4a). Additionally, the diversity of domestic supply is generally higher than the diversity of foreign supply, with the domestic diversity is higher in 68% of cases across all years (Fig 4b). Nevertheless, total imports are still positively associated with supply diversity across all regions (Fig 4c). This suggests that although domestic production diversity is generally higher than the diversity of imported products, trade is still bringing in new species and increasing the diversity of products available on the market. Although imports appear to currently add to supply diversity, it is important for it not to displace domestic production diversity, particularly given that domestic production still contributes more to the diversity of the overall blue food supply.
 

## Other summary stats

![Figure 3: Aquatic resource supply trends and regional patterns. a) Global blue food supply by production source over time. b) Regional blue food supply by production source over time. c) Global blue food domestic versus foreign sourcing over time. d) Regional blue food domestic versus foreign sourcing over time. Note these supply figures include non-food uses.](outputs/fig3.png)

![Figure 4: Relationship between trade and supply diversity. a) Time series of the Shannon diversity of imported blue foods and produced blue foods by region. b) Foreign supply Shannon diversity versus domestic supply Shannon diversity for 2018. The black line represents the 1-to-1 line, such that points falling below the line indicate countries where the domestic supply diversity is greater than the foreign supply diversity. c) Relationship between total imports and overall supply diversity for 2018.](outputs/fig4.png)